Examples of functions

### 2025-01-14 README.Rmd
adding badges

@@

<!-- badges: start -->
<!-- badges: end -->

The goal of criticalvalue is to ...
<!-- TODO aggiungi qualche riga qui -->

@@

You can install the development version of criticalESvalue like so:

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/psicostat/criticalESvalue/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/psicostat/criticalESvalue/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/psicostat/criticalESvalue/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/psicostat/criticalESvalue/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

@@

The goal of `criticalESvalue` is to ...
<!-- TODO aggiungi qualche riga qui -->

@@

You can install the development version of `criticalESvalue` like so:
